### 2014-03-31 paper/designspace.tex
put in bjoern comments

\section{The Design Space of Pipes}
The design space of pipes is large.  By using different types and topologies of pipes and inserting different media into the completed pipes, a variety of inputs and outputs can be located at arbitrary points on the surface of a 3D print.  We describe the space below.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/types.png}
\caption{Types of pipes.  A shows a pair of open tubes filled with copper paint to power an LED.  B shows a return pipe with EL wire threaded through it.  C shows two semi-closed pipes with rubber membranes at their ends.  In D, a rabbit has a fully enclosed chamber to modify its weight.}
\label{fig:pipespace}
\end{figure}

@@

Splitting or mixing pipes offer flexibility in output.  If a maker wished to create a painting device, she might wish to have two system-side pipes feeding in primary-colored red and blue paints which mix in varying ratios, allowing their pigments to combine before purple exits from the device (see Figure \ref{fig:pipespace}).  Splitting can also be useful, for example if our maker wants red paint output in two locations from her painting device, she could have one system-side pipe, but split the pipe into two (see Figure \ref{fig:pipespace}).

>>>>

\section{The Design Space of Pipes}
\bjoern{Budget at most 1.5 columns for this section

 There still some redundancy with the related work section, too}
By using different types and topologies of pipes and inserting different media into the completed pipes, a variety of inputs and outputs can be located at arbitrary points on the surface of a 3D print.  We describe the space below.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/types.png}
\caption{Types of pipes.  A shows a pair of open tubes filled with copper paint to power an LED.  B shows a return pipe with EL wire threaded through it.  C shows two semi-closed pipes with rubber membranes at their ends.  In D, a rabbit has a fully enclosed chamber to modify its weight. \bjoern{Great, but make figure  full column wide}}
\label{fig:pipespace}
\end{figure}

@@

Splitting or mixing pipes offer flexibility in output.  If a maker wished to create a painting device, she might wish to have two system-side pipes feeding in primary-colored red and blue paints which mix in varying ratios, allowing their pigments to combine before purple exits from the device (see Figure \ref{fig:pipespace}).  Splitting can also be useful, for example if our maker wants red paint output in two locations from her painting device, she could have one system-side pipe, but split the pipe into two (see Figure \ref{fig:pipespace}).  \bjoern{??}
